Figures

### 2020-05-15 figures/01_geometry.Rmd
drop class comparison from proxy versus true fig in main text

>>>>

```{r 01_geometry_base, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=4.8, fig.height=2.3}
theme_opts <- cowplot::theme_cowplot() + 
  theme(legend.position = "none", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 11))
text_size <- 3

# distance data
dt         <- readRDS("../data/00_bathy_depth/bathy_pnts.rds")
hypso_pred <- read.csv("../data/00_hypso/hypso_predictors.csv", 
                       stringsAsFactors = FALSE) %>%
  mutate(lagoslakeid = as.character(lagoslakeid))
dt <- left_join(dt, dplyr::select(hypso_pred, lagoslakeid, reservoir_class, shape_class), 
                                  by = c("llid" = "lagoslakeid"))

gg_dist_base <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::filter(dist_deepest < 3200) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter)) + 
  geom_point(size = 1) +
  geom_smooth(method = "lm", se = FALSE) +
  annotate("text", x = 2550, y = 300, label = "R^2 == 0.80",
                                parse = TRUE, size = text_size) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Visual center\ndistance (m)") +
  xlim(0, 3000) +
  theme_opts

# slope data
bp <- readRDS("../data/00_bathy_depth/bathy_pnts.rds")
dt <- read.csv("../data/00_geometry/nearshore.csv", stringsAsFactors = FALSE) %>%
  mutate(llid = as.character(llid))
dt <- left_join(dt, st_drop_geometry(bp), 
                by = "llid") %>%
  dplyr::filter(!is.na(inlake_slope_mean)) %>%
  dplyr::filter(inlake_slope.y < 0.4)
lgus_pred <- read.csv("../data/lagosus_depth_predictors.csv", stringsAsFactors = FALSE) %>%
  mutate(lagoslakeid = as.character(lagoslakeid))
test <- left_join(dt, lgus_pred, by = c("llid" = "lagoslakeid")) %>% 
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::arrange(desc(factor(shape_class, 
                        levels = c("neither", "concave", "convex"))))

gg_slope_base <- ggplot(data = test) + 
  geom_point(aes(slope_mean, inlake_slope.y), size = 1) +
  geom_smooth(aes(slope_mean, inlake_slope.y), method = "lm", se = FALSE) +
  geom_rect(xmin = 0.28, xmax = 0.42, ymin = 0, ymax = 0.05,
  alpha = 1, fill = "white") +
  annotate("text", x = 0.34, y = 0.03, label = "R^2 == 0.17",
                                parse = TRUE, size = text_size) +
  # geom_abline(slope = 1, intercept = 0) +
  xlab("Nearshore slope (mean)") +
  ylab("Inlake slope") +
  labs(color = "") +
  theme_opts

cowplot::plot_grid(
  gg_dist_base, 
  gg_slope_base, 
  rel_widths = c(1, 0.9)
)

### 2020-05-15 manuscript/appendix.Rmd
drop class comparison from proxy versus true fig in main text

>>>>

```{r 01_geometry_grid, fig.cap = "Comparison among lake shape and reservoir classes for A-B) distance to deepest point versus distance to lake visual center and C-D) nearshore slope versus inlake slope. A dashed 1:1 line is shown for comparison. Cross-section shape and reservoir class plots are not identical because not all lakes had a reservoir classification exceeding a 0.75 probability confidence level.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/01_geometry_grid-1.pdf")
```

### 2020-05-15 manuscript/figures.Rmd
drop class comparison from proxy versus true fig in main text

```{r lake_shape, echo=FALSE, out.extra='', fig.align='center', fig.cap="Diagram showing our expectation that slope-based models of lake depth will under predict true depth in convex lakes (left) and over predict true depth in concave lakes (right). Dashed lines represent extrapolated nearshore slope while solid lines represent the lake bottom."}
knitr::include_graphics("../figures/lake_shape.pdf")
```

@@

```{r 01_geometry_grid, fig.cap = "Comparison among lake shape and reservoir classes for A-B) distance to deepest point versus distance to lake visual center and C-D) nearshore slope versus inlake slope. A dashed 1:1 line is shown for comparison. Cross-section shape and reservoir class plots are not identical because not all lakes had a reservoir classification exceeding a 0.75 probability confidence level.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/01_geometry_grid-1.pdf")
```

>>>>

```{r lake_shape, echo=FALSE, out.extra='', fig.align='center', out.width="4in",fig.cap="Diagram showing our expectation that slope-based models of lake depth will under predict true depth in convex lakes (left) and over predict true depth in concave lakes (right). Dashed lines represent extrapolated nearshore slope while solid lines represent the lake bottom."}
knitr::include_graphics("../figures/lake_shape.pdf")
```

@@

```{r 01_geometry_base, fig.cap = "Comparison among proxy and true values of lake geometry for A) distance to deepest point versus distance to lake visual center and B) nearshore slope versus inlake slope. A best-fit line and coefficient of determination is shown to illustrate representativeness.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/01_geometry_base-1.pdf")
```
